BRiM: A Modular Bicycle-Rider Modeling Framework

### 2024-02-09 paper.tex
Updates from Overleaf

Many research grade software packages, like \softwarepackage{SPACAR}, \softwarepackage{Simbody}~\citep{sherman_2011_simbody}, and \softwarepackage{ADAMS}~\citep{ryan_1990_adams}, can efficiently form the EoMs for a multibody system.
One downside of these tools is that the resulting EoMs exist solely in the form of numeric computer code and cannot be accessibly interrogated.
Modern physics engines, like \softwarepackage{MuJoCo}~\citep{todorov_2012_mujoco} and \softwarepackage{Nimble}~\citep{werling_2021_fast}, also offer numerical computation of high-accuracy dynamics.
However, these have not found favor in being applied within the field of bicycle dynamics research, perhaps due to the inability to define every aspect and assumption of a model precisely and because they often focus on aspects not widely applicable to bicycle research, like contact and impact dynamics.

@@

We solved each of the six trajectory tracking optimization problems using \opty{}~\citep{moore_2018_opty}, a Python package for solving optimization problems involving dynamic systems using direct collocation~\citep{betts_2010_practical}. \opty{} is designed with \sympy{} in mind and thus interfaces seamlessly with \brim{}. \opty{} transcribes the optimization problem into a nonlinear programming problem, which is then solved numerically using the interior-point solver \ipopt{}~\citep{biegler_2009_large}. Each optimization problem was transcribed with 100 nodes, resulting in a sample rate of \SI{50}{\hertz}, and the dynamics were collocated using the backward Euler method. \ipopt{}'s default settings were used with the exception of enabling gradient-based scaling.

>>>>

Many research grade software packages, like \softwarepackage{SPACAR}, \softwarepackage{Simbody}~\citep{sherman_2011_simbody}, and \softwarepackage{ADAMS}~\citep{ryan_1990_adams}, efficiently form the EoMs for a multibody system, but these resulting EoMs exist solely in the form of numeric computer code and lack accessibility to be interrogated.
Modern physics engines, like \softwarepackage{MuJoCo}~\citep{todorov_2012_mujoco} and \softwarepackage{Nimble}~\citep{werling_2021_fast}, also offer numerical computation of high-accuracy dynamics.
However, these have not gained traction in bicycle dynamics research, perhaps due to the focus on general applicability with varying assumptions in contact dynamics.
\softwarepackage{FastBike}~\citep{fastbike} simulates single-track vehicles, but remains proprietary, and \softwarepackage{JBike6}~\citep{jbike6} only calculates the eigenvalues of one model.

@@

We solved each of the six trajectory tracking optimization problems using \opty{}~\citep{moore_2018_opty}, a Python package for solving optimization problems involving dynamic systems using direct collocation~\citep{betts_2010_practical}. \opty{} is designed with \sympy{} in mind and thus interfaces seamlessly with \brim{}. \opty{} transcribes the optimization problem into a nonlinear programming problem, which is then solved numerically using the interior-point solver \ipopt{}~\citep{biegler_2009_large}. Each optimization problem was transcribed with 100 nodes, resulting in a node every \SI{0.2}{\second}, and the dynamics were collocated using the backward Euler method. \ipopt{}'s default settings were used with the exception of enabling gradient-based scaling.
